\TheTitle

### 2017-06-12 paper/userstudy.tex
Adding Tree size figure
Adds figure to paper, and to the makefile.

We selected two commits for the participant to draw and summarize by first
determining the size of tree in the first and second quartiles. We found that
between Linux 3.1 and 3.16, the size of the trees in the first quartile only
contained a single node, and that the size of the trees in the second quartile
resulted in trees up to seven nodes. The third quartile contained trees up to 51
nodes, and the fourth quartile contained one tree of 7217 nodes. It is worth
mentioning that the tree sizes in the fourth quartile increase very quickly, as the
next largest tree only contains 4708 nodes, and the third largest tree contains 2349
commits.

>>>>

We selected two commits for the participant to draw and summarize by first
determining the size of tree in the first and second quartiles. We found that
between Linux 3.1 and 3.16, the size of the trees in the first quartile only
contained a single node, and that the size of the trees in the second quartile
resulted in trees up to seven nodes. The third quartile contained trees up to 51
nodes, and the fourth quartile contained one tree of 7217 nodes. It is worth
mentioning that the tree sizes in the fourth quartile increase very quickly, as the
next largest tree only contains 4708 nodes, and the third largest tree contains 2349
commits. We see in figure~\ref{fig:tree_size} how the number of trees decreases as
the size of the tree increases.

\begin{figure}[htpb]
\begin{center}
\caption{Number of merge tree occurrences over size of the merge tree}
\label{fig:tree_size}
\begin{tikzpicture}
  \begin{axis} [
    ylabel=Occurences,
    xlabel=Tree Size,
    grid=both,
    minor x tick num = 1,
    minor y tick num = 1,
    ymode=log
    ]
    \addplot[chartred] table[col sep=comma, x index={1}, y index={0}]{data/tree_size.csv};
  \end{axis}
\end{tikzpicture}
\end{center}
\end{figure}
